---
title: "Team"
author: "John Banta and Karthikcharan Suresh"
date: "9/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Github Information

[Github Repository](https://github.com/jdbanta/ds202_lab2)

Repo owner username: jdbanta

Repo name: ds202_lab2

```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
recent_rating = choco[choco$Review.Date>2011,]
#This gives all the observations that have a review date after 2011 (not including 2011)
unique(recent_rating$Company.Location) # NOTICE: how many countries are listed but how many levels are there? 
#There are 61 levels but there are 54 countries so there are 61 countries originally but only 54 after 2011
recent_rating$Company.Location = droplevels(recent_rating$Company.Location)
#This drops the unused levels so that we only see the used leveles
head(recent_rating)
#This shows the top few rows in the recent_rating dataframe that we made earlier
cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location)
#This makes a table with the review date and company location from the recent_rating dataframe
cross_table
#This displays the table we just made
which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0)
#This shows the location in the array of all the countries that had at least one review in 2012,2013,2014,2015,2016, and 2017
france_recent = subset(recent_rating,Company.Location =='France')
uk_recent = subset(recent_rating,Company.Location =='U.K.')
germany_recent = subset(recent_rating,Company.Location=='Germany')
#These commands make subsets of the recent_rating dataframe and make dataframes for France,UK, and Germany respectively
par(mfrow=c(2,2))
#This makes the graph output window a 2x2 so you can fit 4 graphs
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green')
#This sets a rule for the colors to plot in the next line, so if the individual rating is higher than the median of all the French ratings for that year is blue otherwise it is green
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France") 
#this makes a scatterplot of the Cocoa Percentage and the review date. ylim=c(50,90) sets the range for Y axis. The col command uses the rule made before in the previous line to color each of the observations. Pch=18 makes each individual point a solid diamond. cex=1.5 determines the size of the plotted points. xlab gives the name for the x label and ylab gives the name for the y label. Main gives the name for the whole plot.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18)
#this makes a legend in the bottom right corner. legend=c() gives the names to label the points. col gives the color to assign to each label. PCH=18 once again uses filled in diamonds
color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red')
#This sets a rule for the colors to plot in the next line, so if the individual rating is higher than the median of all the UK ratings for that year is purple otherwise it is red
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK")
#this makes a scatterplot of the Cocoa Percentage and the review date. ylim=c(50,90) sets the range for Y axis. The col command uses the rule made before in the previous line to color each of the observations. Pch=18 makes each individual point a solid diamond. cex=1.5 determines the size of the plotted points. xlab gives the name for the x label and ylab gives the name for the y label. Main gives the name for the whole plot.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18)
#this makes a legend in the bottom right corner. legend=c() gives the names to label the points. col gives the color to assign to each label. PCH=18 once again uses filled in diamonds
color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow')
#This sets a rule for the colors to plot in the next line, so if the individual rating is higher than the median of all the UK ratings for that year is orange otherwise it is yellow
plot(germany_recent$Cocoa.Pct ~ germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany")
#this makes a scatterplot of the Cocoa Percentage and the review date. ylim=c(50,90) sets the range for Y axis. The col command uses the rule made before in the previous line to color each of the observations. Pch=18 makes each individual point a solid diamond. cex=1.5 determines the size of the plotted points. xlab gives the name for the x label and ylab gives the name for the y label. Main gives the name for the whole plot.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18)
#this makes a legend in the bottom right corner. legend=c() gives the names to label the points. col gives the color to assign to each label. PCH=18 once again uses filled in diamonds
```

2.
Plot could probably be improved, to me, by saying in the legend that ratings are higher or lower than median. Also for the orange and yellow plot, use different colors because they are kind of hard to see. 

3.
the number of ratings tends to increase from 2006 to 2015 and then fall lower!

```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
Rating <- table(choco$Rating, choco$Review.Date)
barplot(colSums(Rating))
```

4.
```{r}
country <- table(choco$Rating, choco$Company.Location)
country1 <- colSums(country)
sort(country1, decreasing = TRUE)
list1 <- cbind(country[, "U.S.A."], country[, "France"], country[, "Canada"])
list1
country2 <- data.frame(list1)
country2
list2 <- sort(unique(choco$Rating), decreasing = FALSE)
plot(list2, country2$X1, pch = 1, col = 'green', xlab = "rating", ylab = 'USA')
plot(list2, country2$X2, pch = 2, col = 'blue', xlab = "rating", ylab = 'France')
plot(list2, country2$X3, pch = 3,col = 'pink', xlab = "rating", ylab = 'Canada')
```

The ratings look like they are approximately normally distributed with mean 3.



5.
Does number of cocoa percentage and review date have a relationship?

6.
The number of cocoa percentage also tends to increase from 2006 to 2015 and then fall lower!
```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
Cocoa.Pct <- table(choco$Cocoa.Pct, choco$Review.Date)
barplot(colSums(Cocoa.Pct))
```
